Project Proposal: Monaural Single-Source Speaker Separation

### 2018-10-07 paper/e511-proposal.tex
Project proposal.

\documentclass{sig-alternate}

@@

Our initial step will be to apply the non-negative matrix
factorization technique illustrated in the class materials to perform
a baseline for this source separation problem. From there, we intend
to explore a neural network model using PyTorch to implement
Permutation Invariant Training (PIT) from
\cite{DBLP:journals/corr/KolbaekYTJ17} or utterance-level Permutation
Invariant Training (uPIT) from
\cite{DBLP:journals/corr/YuKTJ16}
as these seem to be the latest approaches to
single source sound separation in the academic literature. The call
center recordings are not currently labeled, so we propose creating
our own test and training dataset by mixing single-speaker recordings
from either the TIMIT or WSJ0 recordings. The literature mentions the
WSJ0-2mix data set that was used in
\cite{DBLP:journals/corr/HersheyCRW15} the seminal Deep Clustering
(DPCL) paper but we have yet to find a specification for how to
generate this dataset.

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{e511_proposal}
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
\end{document}

>>>>

\documentclass{e511-project}

@@

Our initial step will be to apply the non-negative matrix
factorization technique illustrated in the class materials to perform
a baseline for this source separation problem. From there, we intend
to explore a neural network model using PyTorch to implement
Permutation Invariant Training (PIT) from
\cite{DBLP:journals/corr/KolbaekYTJ17} or utterance-level Permutation
Invariant Training (uPIT) from
\cite{DBLP:journals/corr/YuKTJ16}
as these seem to be the latest approaches to
single source speaker separation in the academic literature. The call
center recordings are not currently labeled, so we propose creating
our own test and training dataset by mixing single-speaker recordings
from either the TIMIT \cite{garofolo:timit} or WSJ0 
\cite{garofolo:wsj0} recordings.
The literature mentions the WSJ0-2mix data set that was used in
\cite{DBLP:journals/corr/HersheyCRW15} the seminal Deep Clustering
(DPCL) paper but we have yet to find a detailed specification for how to
generate this dataset.

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{e511-proposal}
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
\end{document}
